Kepler's Demographic Cliff: Ages of Young Stars and Planets in the Kepler Field

### 2024-05-20 paper/ms.tex
ms: WIP cluster age refactor

@@

\appendix
\section{Literature Age Scale Comparison}
\label{app:litagecomparison}

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.98\textwidth]{merged_lit_ages_vs_cluster_ages.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Literature age scale comparison.}
    Each point denotes the reported age of a star observed by Kepler,
    normalized by the age of a stellar ensemble in which the star
    is a candidate member.
    We used memberships from spatio-kinematic estimates in the
    literature.
    Rows show the available stellar ensembles, and columns show the
    various age-measurement techniques described in
    Appendix~\ref{app:litagecomparison}.
    Stars are sorted according to their median reported ages, and
    clusters are sorted by descending richness.
    Note that the horizontal axis is logarithmic; the first dotted line
    to the right of unity corresponds to a reported age ten times older
    than the cluster age.
	}
	\label{fig:agescalecompone}
\end{figure*}

>>>>

\section{Cluster Age Comparison}
\label{sec:litagecomparison}

Stars that formed in the same birth cluster, at approximately the same time,
are the gold standard for the astronomical age scale
\citep{Soderblom10}.
Before Gaia, only a handful of $\gtrsim$1\,Gyr open clusters
were known in the Kepler field.

The gold standard for stellar ages comes from open clusters

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.98\textwidth]{olympic_merged_lit_ages_vs_cluster_ages.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Literature age comparison.}
		Each point denotes a reported age,
		normalized by the age of a stellar ensemble in which the star
		is a candidate member.
		We used candidate cluster members as reported by previous studies based on spatial and kinematic
		information.  Although some field interlopers may be present in the 
		membership lists,
		any outliers can be compared between different methods on a
		relative basis.
		The number of stars in any given cluster follows by crossmatching every study against
		this fixed cluster list; certain methods report ages for more stars than others.
		Horizontal scatter is artificially added to visually
		clarify the statistical age uncertainties.
	}
	\label{fig:agescalecompone}
\end{figure*}

@@
